DraftFunctions

### 2021-05-11 R/DraftFunctions.Rmd
Tree heights fitting models

```{r}
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
```

@@

```{r TreeHeight}
library(BIOMASS)
library(knitr)
# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
# 3 options :
# - get my tree heights from the location (from continent or region specific model, or from coordinates)
# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.

RegionTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
# GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela

n <- length(Paracou6_2016$CircCor)
coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
CoordTreeHeight <- retrieveH(D = Paracou6_2016$CircCor, coord = coord) #by coordinates (Chave et al. (2012))

result <- modelHD(D = , H = , useWeight = TRUE) #from Guyanese trees heights data
kable(result)
# Compute the local H-D model with the lowest RSE (Root Squared Error)
selectedHDmodel <- modelHD(D = , H = , method = "log2", useWeight = TRUE)

predictHeight(CircCor, model)

>>>>

```{r}
library(Maria)
library(readr)
library(dplyr)
library(tibble)
library(tidyr)
```

@@

```{r TreeHeight}
library(BIOMASS)
library(knitr)
if (!("DBH" %in% names(Paracou6_2016))) {add_column(Paracou6_2016, DBH = NA) #if DBH (cm) doesn't exist create it
   Paracou6_2016$DBH = Paracou6_2016$CircCorr/pi} # and compute it
# TreeHeight = hauteur de l’arbre (H) (en mètre) (BIOMASS package)
# 3 options :
# - get my tree heights from the location (from continent or region specific model, or from coordinates)
# - from other Guyanese trees heights data, fit different H-D models, select the best and apply on my data.

RegionTreeHeight <- retrieveH(D = Paracou6_2016$DBH, region = "GuianaShield") #continent or region specific model (Feldpaush et al. (2012))
# GuianaShield = Guyana, French Guiana (piste St Elie (Chave 2005)), Venezuela

n <- length(Paracou6_2016$CircCor)
coord <- cbind(long = rep(-52.92, n), lat = rep(5.27, n)) # Paracou P6 coordinates
CoordTreeHeight <- retrieveH(D = Paracou6_2016$DBH, coord = coord) #by coordinates (Chave et al. (2012))

# Just with Nouragues data (measurement: laser rangefinder):
ModelsresultNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  useWeight = TRUE
)
kable(ModelsresultNouraguesdata) #log2 has the lowest RSE (4.222718) (Root Squared Error)
HDmodelNouraguesdata <- modelHD(
  D = NouraguesHD$D,
  H = NouraguesHD$H,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
TreeHeightEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelNouraguesdata
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
mutate(TreeHeight = TreeHeightEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form

# Different guyanese data:
TreeheightGuyafordata <- read_delim("D:/VSC Kourou/DATA/TreeheightGuyafordata.csv", 
    ";", escape_double = FALSE, col_types = cols(Circ = col_number(), 
        CircCorr = col_number(), Hauteur = col_number()), 
    locale = locale(encoding = "Latin1"), 
    trim_ws = TRUE) %>% 
  # filter(!(HeightHow == "Visual Estimate" | HeightHow == "Visual estimate"))
    filter(HeightHow == "Sine Method (Larjavaara & Muller-Landau 2013) with Trimble LaserAce 1000 Rangefinder")
if (!("DBH" %in% names(TreeheightGuyafordata))) {add_column(TreeheightGuyafordata, DBH = NA) #if DBH (cm) doesn't exist create it
   TreeheightGuyafordata$DBH = TreeheightGuyafordata$CircCorr/pi} # and compute it

unique(TreeheightGuyafordata$HeightHow)

ModelsresultGuiana <- modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  useWeight = TRUE
)
kable(ModelsresultGuiana) #log2 has the lowest RSE (4.749107 with all data, 4.316927 without "Visual E/estimate", 3.059860 with just "Sine Method")
#Don't forget, you have the model form, and its parameters, and there are different according to the data.

HDmodelGuiana <- modelHD(
  D = TreeheightGuyafordata$DBH,
  H = TreeheightGuyafordata$Hauteur,
  method = "log2", # Compute the local H-D model with the lowest RSE.
  useWeight = TRUE
)
TreeHeightGuianaEstimation <- retrieveH(
  D = Paracou6_2016$DBH,
  model = HDmodelGuiana
)
## Put these tree heights estimations in the inventory
Paracou6_2016TreeHeight <- Paracou6_2016 %>% 
mutate(TreeHeight = TreeHeightGuianaEstimation$H)
plot(Paracou6_2016TreeHeight$DBH, Paracou6_2016TreeHeight$TreeHeight)#amazing !! It's a log2 form
